\documentclass[10pt]{article}
\title{ Use case Project}
\begin{document}
\maketitle
\tableofcontents

\section{Team: Raptors}
\begin{enumerate}
\item Kavaljeet Singh :C0748291
\item Gurkeet Puri: C0748159
\item Inderdeep Singh: C0753889
\item Rajat Parbhakar: C0749084
\item Lovepreet Singh: C0767429
\end{enumerate}

\section{Use Case 1: The Statement Of Work}
\subsection{Goal}
A Statement of work is firstly there to show our project stakeholders about our requirements.
\subsection{Actors}
Project Manager and team members.
\subsection{Scenario}
\begin{enumerate}
\item  Direct access to the Web Application via URL  for users.
\item The user will then be required to register to our software.
\item Then, the User will get page showing  his username and password.
\item The user can now access the software.
\item The user will get the overall information of our software after logging in.
\end{enumerate

\section{USE Case 2: WBS(Work Breakdown Structure)}
\subsection{Goal}
To breakdown our project into smaller tasks so that it becomes easier to control it and work on it.
\subsection{Actors}
Project Manager
\subsection{Scenario}
\begin{enumerate}
\item The leader needs to split his work into smaller tasks.
\item Then he can assign tasks to all the members of the team.
\item The team members then evaluate and design the project as per the requirements.
\item Finally, they come up with several ideas that leads them in the execution of the project.
\end{enumerate}

\section{USE Case 3: Building Resource Register}
\subsection{Goal}
Benefits to the audience.
\subsection{Actors}
Project Manager 
\subsection{Scenario}

\begin{enumerate}
\item The Project Manager has to make submission  the project to the authority to publish it on internet.
\item Then the authority will  make the decision about it after checking.
\item At the end, to get access on the internet , we can make it visible .

\end{enumerate}

\end{document}
© 2019 GitHu